Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-01 paper/paper.qmd
Update paper.qmd
added reference to intro

Understanding voter sentiment is essential for both political campaigns
and analysts, especially with the upcoming U.S. election on the horizon.
Public opinion is highly dynamic and can change swiftly due to various
influences, including media coverage, campaign tactics, and major
events. This study aims to forecast the percentage of support for Kamala
Harris, offering insights into the elements that shape voter preferences
as the election nears. By examining data from multiple polling sources,
we intend to pinpoint the key factors influencing support, such as the
poll's end date, the polling organization, geographic location, and the
poll's score. Our research seeks to fill a gap in existing literature
that often fails to address the complexities of polling data, thereby
enhancing our understanding of voter behavior within the electoral
context.

@@

The main focus of our analysis is the percentage of support for Harris,
which we will model using various predictor variables. We are
particularly interested in how the end date, polling organization,
state, and poll score affect voter support. Using a linear regression
framework, we can quantify the relationships between these predictors
and the support outcome, providing clarity on how each factor influences
overall support for Harris. By estimating the coefficients for each
predictor, we aim to draw significant conclusions about their respective
impacts on voter sentiment.

>>>>

Understanding voter sentiment is essential for both political campaigns
and analysts, especially with the upcoming U.S. election on the horizon.
Public opinion is highly dynamic and can change swiftly due to various
influences, including media coverage, campaign tactics, and major
events. This study aims to forecast the percentage of support for Kamala
Harris, offering insights into the elements that shape voter preferences
as the election nears. By examining data from multiple polling sources,
we intend to pinpoint the key factors influencing support, such as the
poll's end date, the polling organization, geographic location, and the
poll's score.

Research by Gelman and King (1993) underscores that while polls can exhibit
variability over a campaign period, they can provide reliable predictions 
when adjusted for temporal changes and fundamental factors. Additionally,
Erikson and Wlezien (2008) highlight the importance of timing in polling,
showing that data closer to election day tends to stabilize and therefore
becomes more predictive. Our research seeks to fill a gap in existing
literature that often fails to address the complexities of polling
data, thereby enhancing our understanding of voter behavior within the
electoral context.

@@

The main focus of our analysis is the percentage of support for Harris,
which we will model using various predictor variables. We are
particularly interested in how the end date, polling organization,
state, and poll score affect voter support. Using a linear regression
framework, we can quantify the relationships between these predictors
and the support outcome, providing clarity on how each factor influences
overall support for Harris. As Silver (2012) argues, leveraging aggregated
data from multiple reputable sources and adjusting for sample quality
and methodology is crucial for achieving accurate predictions.
By estimating the coefficients for each predictor, we aim to draw
significant conclusions about their respective impacts on voter
sentiment.
